Just Add IFC! A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-03-02 paper/extensions.tex
donezo with the extensions

\paragraph{Labeled mutable references/variables/channels}
%
In a similar manner, extending the

>>>>

\paragraph{Labeled mutable references/variables/channels}
%
Extending the calculus with other labeled features, such as
references, mutable variables (MVars)~\tocite{CH96}, or channels,
follows in a similar way.
%
In these cases, however, we must keep track of the additional state
(as opposed to the labeled value case which requires no additional
bookkeeping).
%
While we can modify the IFC calculus to add such labeled state to each
individual task, adding it to the system state |iS| leads to more
interesting use cases.
%
Specifically, by amending |iS|, as in~\cite{lio,
stefan;addressing-covert}, we can allow threads to use these
constructs to synchronize, or communicate with constructs other than
|send|/|recv| in a safe manner.
%
For example, when extending the calculus with labeled references, |iS|
additionally contains a store that maps addresses to |(il, tv)| pairs
which can be read and written to by different tasks through a labeled
|ref| implementations.
%
Since such labeled constructs have also been considered before in other
concurrent systems, we do not discuss them further.
